Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-11-05 Paper.Rmd
minor fixes

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] . Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Any website which offer online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data either from websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon were used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

@@

Online Consumer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].

@@

Exploratory Data Analysis (EDA) has no set of procedures to be followed. The way EDA is conducted almost always depends on the context of the research. @jebb2017 discusses that EDA encourages scientific replication if done properly. As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value. I also think that readers or fellow researchers might build a better intuition about the discussion and what goes into the model in this study.

@@

@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

In order to decrease the uncertainty in the most optimal way, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length. After some point more information can cause confusion and may render the review unfocused [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. This might decrease the average responsivess of the Perceived Helpfulness to the Review Length. However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

>>>>

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] . Search goods, by nature, have traits that can be observed objectively before buying (e.g., GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (e.g., One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Any website which offer online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data either from websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs (Application Programming Interface) and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon were used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

@@

Online Consumer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (e.g., personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (e.g., writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].

@@

Exploratory Data Analysis (EDA) has no set of procedures to be followed. The way EDA is conducted almost always depends on the context of the research. @jebb2017 discusses that EDA encourages scientific replication if done properly. This section is going to be constructed with two notions in mind:

1.  Transparent data sharing for the sake of increased reproducibility value

2.  Helping readers build a better intuition about the model and its components through transparency

@@

@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. For instance, one person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

In order to decrease the uncertainty in the most optimal way, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (e.g., storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length. After some point more information can cause confusion and may render the review unfocused [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. This might decrease the average responsiveness of the Perceived Helpfulness to the Review Length. However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:
